Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-04-20 manuscript/manuscript.Rmd
updates forecast horizon plot

Data accessibility
------------------
Chart-quadrat data available from *Ecological Archives* at http://esapubs.org/archive/ecol/E092/143/.
All code to reproduce our work is available on Dryad (link) and GitHub (https://github.com/atredennick/MicroMesoForecast).

@@

\setcounter{page}{29}

Tables
------
```{r table_1,results='asis',message=FALSE, comment=NA, echo=FALSE, eval=F}
####
##  Make a table for average residual from each model and year effects structure
####

##  IPM results
# Read in data
setwd("/Users/atredenn/Repos/MicroMesoForecast/manuscript/")
ipm_onestep <- readRDS("../analysis/ipm/simulations/results/one_step_validation/ipm_loyo_forecasts_combined.rds")
# Remove predictions >1 for fair comparison to [0,1] truncated quad model
resets <- which(ipm_onestep[,"cover.t1"]>1)
ipm_onestep[resets, "cover.t1"] <- 1
# Average predictions over quad-year reps
avg_ipm <- ddply(ipm_onestep, .(species, quad, t1), summarise,
                 avg_prediction = median(cover.t1),
                 observation = mean(cover.t0),
                 quant_dist = quantile(cover.t1*100, probs = 0.95) - quantile(cover.t1, probs = 0.05))
# Calculate error
avg_ipm$error <- avg_ipm$observation*100 - avg_ipm$avg_prediction*100
# Aggregate over species
ipmstats <- ddply(avg_ipm, .(species), summarise,
                  mae = mean(abs(error)),
                  mean_cover = mean(observation*100),
                  quant_dist = mean(quant_dist))
ipmstats$model <- "IPM"

mae_ps <- melt(mae_pvals)

stats_table <- rbind(ipmstats, qbmstats)
stats_table <- stats_table[ order(stats_table[,"species"]), ]
stats_table <- stats_table[,c("species", "model", "mae",
                              "quant_dist","mean_cover")]

colnames(stats_table) <- c("Species", "Model", "MAE", "90% Distance", "Mean Obs. Cover")
print.xtable(xtable(stats_table, caption = "Accuracy (mean absolute error, MAE) and precision (90\\% Distance) of out of sample predictions. Forecasts were made without random year effects; only climate covariates could explain year-to-year variation. 90\\% Distance refers to the average distance between the upper and lower 90th percentiles of the 100 predicted values for each quadrat-year combination."),type="latex", comment=FALSE,
             include.rownames=FALSE, caption.placement="top")
```

>>>>

@@

Tables
------

\begin{table}[ht]
\centering
\caption{Accuracy (mean absolute error, MAE) and precision (90\% Distance) 
                  of out of sample predictions. Forecasts were made without random 
                  year effects; only climate covariates could explain year-to-year 
                  variation. 90\% Distance refers to the average distance between the 
                  upper and lower 90th percentiles of the 100 predicted values for 
                  each quadrat-year combination.} 
\begin{tabular}{llrrr}
  \hline
Species & Model & MAE & 90\% Distance & Mean Obs. Cover \\ 
  \hline
BOGR & IPM & 4.03 & 24.74 & 9.43 \\ 
  BOGR & QBM & 2.80 & 29.46 & 8.35 \\ 
  HECO & IPM & 0.34 & 1.87 & 1.15 \\ 
  HECO & QBM & 0.29 & 5.53 & 1.18 \\ 
  PASM & IPM & 0.14 & 0.50 & 0.42 \\ 
  PASM & QBM & 0.17 & 1.57 & 0.42 \\ 
  POSE & IPM & 0.45 & 1.63 & 1.25 \\ 
  POSE & QBM & 0.41 & 3.51 & 1.27 \\ 
   \hline
\end{tabular}
\end{table}
